---
title: "Reading data from the web"
author: "Jeff Goldsmith"
date: "10/11/2018"
output: github_document
---

```{r, include = FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_bw() + theme(legend.position = "bottom"))
```

Load some packages.

```{r}
library(rvest)
library(httr)
```

## Scrape a table

First get the HTML. Read HTML is in the rvest package. 

```{r}
url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"
drug_use_xml = read_html(url)

drug_use_xml

```

Get the tables from the HTML. Pulls all the HTML objects labelled table. [[1]] gives the first element of a list. This can be changed to retrieve any of the subsequent tables. Slice lets you access rows of a dataset by number. 

```{r}
drug_use_xml %>%
  html_nodes(css = "table") %>% 
  .[[1]] %>% 
  html_table() %>% 
  slice(-1) %>% 
  as_tibble() %>% View
```

## Learning assessment

```{r}
url2 = "https://www.bestplaces.net/cost_of_living/city/new_york/new_york" 
cost_living_xml = read_html(url2)

cost_living_xml %>% 
  html_nodes(css = "table") %>% 
  .[[1]] %>% 
  html_table(header = TRUE)

```

## CSS Selectors

Scraping data from IMDB: 

```{r}
hpsaga_html = read_html("https://www.imdb.com/list/ls000630791/")
titles = hpsaga_html %>% 
  html_nodes(css = ".lister-item-header a") %>% 
  html_text()

money = hpsaga_html %>% 
  html_nodes(css = ".text-muted .ghost~ .text-muted+ span") %>% 
  html_text()

hpsaga_df = tibble(
  title = titles,
  gross_rev = money
)
```


```{r}
nap_dyn_html = read_html("https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1")
nap_titles = nap_dyn_html %>% 
  html_nodes(css = "#cm_cr-review_list .a-color-base") %>% 
  html_text()

star = nap_dyn_html %>% 
  html_nodes(css = "#cm_cr-review_list .review-rating") %>% 
  html_text()

nap_dyn_df = tibble(
  title = nap_titles,
  star = star
)

```

## Using an API

Get the water data. This line of code can be reproduced by sending it to others because it is linking back to an API URL. 

```{r}
nyc_water = GET("https://data.cityofnewyork.us/resource/waf7-5gvc.csv") %>% 
  content("parse")

```


